Protecting Private Data in the Cloud: A Path Oblivious RAM Protocol

### 2014-11-25 paper/paper.tex
converted all figures to pdfs, added all captions and labels

\begin{figure}
\begin{center}
  \includegraphics[width=6cm]{220.png}
  \caption{Example of binary tree with blocks of data. \textcolor{red}{put the
  whole ORAM architecture here.}}
  \label{fig:bintree}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
  \noindent\includegraphics[width=8.5cm]{310.png}
  \caption{\textcolor{red}{should have a caption}}
  \label{fig:bigpic}
\end{center}
\end{figure}

@@

\begin{center}
\noindent\includegraphics[width=8cm]{320.png}
\end{center}

@@

For all experiments, the parameters were kept at constant values (unless we were testing that parameter). The ORAM tree size (if auto resizing is off) was dependent on the amount of data written to it, twice the total file size. Segment size was 64 KB (optimal as indicated by Figure 5-2) with bucket sizes of z = 3.  The maximum stash size was 100. The utilization ratio that triggers tree growth was 0.45 and for tree shrinkage 0.55. We use throughput as the performance metric, which is a measurement of how fast files can be read from and written to our ORAM-enabled Dropbox. It is expressed in bits per second or multiples of it. For our experiments we use megabytes per second (MB/s).

For all the experiments except the one in Section 5.5, we utilize a distribution of files of various sizes to better simulate the contents/actions of a “real” file system, by reading/writing 1000 files based upon this cumulative distribution. This file distribution was chosen from previous work done on file system workloads \cite{roselli2000comparison}, and is reproduced below in Figure 5-1.

\begin{center}
\noindent\includegraphics[width=8.5cm]{510.png}
\end{center}

\subsection{Optimal Segment Size}
\begin{center}
\noindent\includegraphics[width=8.5cm]{520.png}
\end{center}

@@

\subsection{Initial ORAM Efficiency}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash}p{#1}}
\begin{center}
  \noindent\begin{tabular}{| C{1.5cm} | C{3cm} | C{2.5cm} |}
  \hline
  \bf{Disk} & \bf{Disk + Encryption} & \bf{Disk + ORAM} \\
  \hline
  42.13 & 24.42 & 0.66 \\
  \hline
\end{tabular}
\end{center}

@@

\subsection{Multi-Block Fetching}
\begin{center}
\noindent\includegraphics[width=8.5cm]{540.png}
\end{center}

@@

\subsection{Block Packing}
\begin{center}
\noindent\includegraphics[width=4.25cm]{550.png}\includegraphics[width=4.25cm]{551.png}
\end{center}

@@

\subsection{Dynamic Growing and Shrinking}
\begin{center}
\noindent\includegraphics[width=8.5cm]{560.png}
\end{center}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=6cm]{220.pdf}
  \caption{Example of binary tree with blocks of data.}
  \label{fig:bintree}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
  \noindent\includegraphics[width=8.5cm]{310.pdf}
  \caption{Basic structure of our Path ORAM implementation}
  \label{fig:metadiag}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\noindent\includegraphics[width=8cm]{320.pdf}
\caption{User File System}
\label{fig:userfilesys}
\end{center}
\end{figure}

@@

For all experiments, the parameters were kept at constant values (unless we were testing that parameter). The ORAM tree size (if auto resizing is off) was dependent on the amount of data written to it, twice the total file size. Segment size was 64 KB (optimal as indicated by {\bf Figure \ref{fig:segsize}}) with bucket sizes of z = 3.  The maximum stash size was 100. The utilization ratio that triggers tree growth was 0.45 and for tree shrinkage 0.55. We use throughput as the performance metric, which is a measurement of how fast files can be read from and written to our ORAM-enabled Dropbox. It is expressed in bits per second or multiples of it. For our experiments we use megabytes per second (MB/s).

For all the experiments except the one in {\bf Section}, we utilize a distribution of files of various sizes to better simulate the contents/actions of a “real” file system, by reading/writing 1000 files based upon this cumulative distribution. This file distribution was chosen from previous work done on file system workloads \cite{roselli2000comparison}, and is reproduced in {\bf Figure \ref{fig:distfun}}.

\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{510.pdf}
\caption{File Distribution Function}
\label{fig:distfun}
\end{center}
\end{figure}

\subsection{Optimal Segment Size}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{520.pdf}
\caption{Segment Size Sweep Study}
\label{fig:segsize}
\end{center}
\end{figure}

@@

\subsection{Initial ORAM Efficiency}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash}p{#1}}
\begin{figure}
\begin{center}
  \noindent\begin{tabular}{| C{1.5cm} | C{3cm} | C{2.5cm} |}
  \hline
  \bf{Disk} & \bf{Disk + Encryption} & \bf{Disk + ORAM} \\
  \hline
  42.13 & 24.42 & 0.66 \\
  \hline
\end{tabular}
\caption{Baseline Comparisons (MB/s)}
\label{tab:baseline}
\end{center}
\end{figure}

@@

\subsection{Multi-Block Fetching}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{540.pdf}
\caption{Multi-Block Evaluation}
\label{fig:multiblock}
\end{center}
\end{figure}

@@

\subsection{Block Packing}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=4cm]{550.pdf}\includegraphics[width=4cm]{551.pdf}
\caption{Block Packing Evaluations}
\label{fig:blockpack}
\end{center}
\end{figure}

@@

\subsection{Dynamic Growing and Shrinking}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{560.pdf}
\caption{Tree Resizing Demonstration}
\label{fig:resizing}
\end{center}
\end{figure}
